####
## Download all occurances of Eucs from ALA and get the matching MAP and MAT
## Then remake Fig 1 in Hughes et al. (1996) Climatic Range Sizes of
## Eucalyptus Species in Relation to Future Climate Change. Global Ecology and
## Biogeography Letters, 5, 23-29
##
## Date: 15/11/2017
## Author: Martin De Kauwe
####
```{r}
library(ALA4R)
library(dplyr)
```
^works



# for every species, get range of MAT
```{r}
get_MAT_range <- function(species_name, sep){
  counts <- sep[,species_name]

  # Exclude single occurrence records
  mats <- sep$worldClimTemperatureAnnualMean[which(counts > 1)]
  mats <- mats[is.finite(mats)]

  if (length(mats)) {
    # Exclude values where the MAT min is 0, not sure what that implies
    if (min(mats, na.rm=TRUE) < 0.001) {
      NA
    } else {
      max(mats, na.rm=TRUE) - min(mats, na.rm=TRUE)
      if (max(mats, na.rm=TRUE) - min(mats, na.rm=TRUE) >= 10.) {
        print(c(trimws(species_name), sum(counts), min(mats, na.rm=TRUE), max(mats, na.rm=TRUE)))
      }
    }
  } else {
    NA
  }
}
```
^works




# Get all the counts of Eucs occurrences
```{r}
ss = sites_by_species("genus:Eucalyptus",
                      wkt="POLYGON((110 -45,155 -45,155 -10,110 -10,110 -45))",
                      gridsize=0.5)

ss <- occurrences('genus:Eucalyptus',
                  wkt="POLYGON((110 -45,155 -45,155 -10,110 -10,110 -45))",
                  fq='-basis_of_record:PreservedSpecimen',
                  fields=c('scientificName', 'longitude', 'latitude', 'el862'),
                  download_reason_id=7)$data
```
^ Error on line 49. ALA server gives back 304 error code

```{r}
#insert new ALA data
ala_temp <- read.csv("./ala_w_temp.csv")
ala_s <- ala_temp %>%
  select('Species','Latitude','Longitude','Temperature...annual.range..Bio07.') %>%
  dplyr::rename(
    'species' = 'Species' ,
    'latitude' = 'Latitude' ,
    'longitude' = 'Longitude', 
    'temp_range' = 'Temperature...annual.range..Bio07.'


#randomly sample to be under 50,000 limit of intersect_points function on line 87

ss<-ala_s[sample(NROW(ala_s), 49999),];

ss <- mutate(ala_subs, longitude = 'longitude' + 0.25,
             latitude = 'latitude' + 0.25)
```
^ line 63 I put in my own dataset



# Get bioclimatic stuff
```{r}
env_layers = c("WorldClim: Temperature - annual mean",
               "WorldClim: Precipitation - annual")
ep = intersect_points(ss[, c("latitude","longitude")], env_layers)
ep$worldClimTemperatureAnnualMean = ep$worldClimTemperatureAnnualMean / 10.0

# For each species figure out the temperature range it occurs in
sep <- cbind(ss, ep)
species_names <- grep("eucalyptus", names(sep), value=TRUE)
temp_range <- sapply(ss$species, get_MAT_range, sep=" ")

# Exclude single point data, where there is no range, presumably botanical gardens
temp_range <- temp_range[is.finite(temp_range),]
temp_range <- temp_range[temp_range > 0.0]
```
^line 96 gives error because temp_range is list of 0

```{r}

#two attempts to put the temp range colums into list format, neither work properly
temp_range <- split(temp_range, seq(nrow(ss$species)))
temp_range <- as.list(as.data.frame(t(ss)))


```

```{r}



tmax <- getData("worldclim",var="tmax",res=10)
gain(tmax)=0.1

lats <- c(9.093028 , 9.396111, 9.161417)
lons <- c(-11.7235, -11.72975, -11.709417)
coords <- data.frame(x=lons,y=lats)
points <- SpatialPoints(coords)
values <- extract(tmax,points)
ss <- cbind.data.frame(coordinates(points),values)
ss$max <-apply(X=df, MARGIN=1, FUN=max)
ss

library(sp)
library(raster)
tmax <- getData("worldclim",var="tmax",res=10)
gain(tmax)=0.1

lats <- c(9.093028 , 9.396111, 9.161417)
lons <- c(-11.7235, -11.72975, -11.709417)
coords <- data.frame(x=lons,y=lats)
points <- SpatialPoints(coords, proj4string = tmax@crs)
values <- extract(tmax,points)
df <- cbind.data.frame(coordinates(points),values)
df$max <-apply(X=df, MARGIN=1, FUN=max)

```

```{r}
colnames(ALA_data)
ALA_clim <- ALA_data %>%
  dplyr::select('Species','Latitude','Longitude','Temperature...annual.mean..Bio01.','Fraction.of.Photosynthetically.Active.Radiation..fPAR.','Temperature...annual.max.mean','Gross.Primary.Productivity..2012.03.13.','Evaporation...average','Distance...to.coast','Elevation.') %>%
  dplyr::rename(
    'GPP' ='Gross.Primary.Productivity..2012.03.13.',
    'annual_Ta_max' = 'Temperature...annual.max.mean',
    'fPAR' = 'Fraction.of.Photosynthetically.Active.Radiation..fPAR.',
    'evaporation' = 'Evaporation...average',
    'distance_to_coast' = 'Distance...to.coast',
    'annual_Ta' = 'Temperature...annual.mean..Bio01.',
    'elevation' = 'Elevation.'
  )
```








# Figure out the histogram
```{r}
bins <- seq(1, 11, by=1)
bin_count <- vector(length=length(bins))
for (b in 1:length(bins)) {
  if (b == 1) {
    bin_count[b] <- length(df[df <= 1.0])
  } else if (b==length(bins)) {
    bin_count[b] <- length(df[df > bins[b-1]])
  } else {
    bin_count[b] <- length(df[(df > bins[b-1]) &
                                      (df <= bins[b])])
  }
}

total <- sum(bin_count)
bin_count <- bin_count / total * 100.

pdf("Hughes_figure_ALA.pdf", width=9, height=6)
names(bin_count) <- c("<1", "1-2", "2-3", "3-4", "4-5", "5-6", "6-7", "7-8",
                      "8-9", "9-10", ">10")
xlab <- expression("Mean annual temperature range " ( degree~C))
ylab <- "% Species"
barplot(bin_count, xlab=xlab, ylab=ylab)

```
^ broken, gives either error because of temp_range list being list of zero, message saying "null device 1"

